Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to simulated data: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
\centering
{\includegraphics[width=.33\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
{\includegraphics[width=.33\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
{\includegraphics[width=.33\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
\end{frame}
}

@@

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
	\begin{frame}{Rotterdam: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
		\centering
\visible<1->{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_Rotterdam}}
\visible<2->{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_Rotterdam}}
\visible<3->{\includegraphics[width=.32\linewidth]{../Figures/PNG/Entropy_AO_Rotterdam_1024}}
	\end{frame}
}

>>>>

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to simulated data: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
\centering
{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
{\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
\end{frame}
}

@@

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
	\begin{frame}{Rotterdam: test statistics $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$}
		\centering
\visible<1->{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_Rotterdam}}
\visible<2->{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_Rotterdam}}
\visible<3->{\includegraphics[width=.32\linewidth]{../Figures/PNG/Entropy_AO_Rotterdam_1024}}
	\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
	\begin{frame}{Rotterdam: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
		\centering
		\visible<1->{\includegraphics[width=45mm]{../Figures/PNG/cv_pvalues_Rotterdam} }
		\visible<2->{\includegraphics[width=45mm]{../Figures/PNG/mnad_p_values_Rotterdam} }
		\visible<3->{\includegraphics[width=45mm]{../Figures/PNG/H_pvalue_AO_Rotterdam_1024} }
	\end{frame}
}
